What do incoming university students believe about open science practices in

### 2021-10-18 analysis/Manuscript.Rmd
JB edits to results part 1

In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm. However, the extent to which participants endorsed open science norms varied very substantially across different practices. Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing 'agree'). They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items were all between 3.5 and 4. On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.

<!--MW: The paragraphs above contain some numeric info that's written in manually rather than being R outputs (e.g., "three", "seven") 
Not sure if that's a worry.
-->

@@

# clean up the tibble                          
practice_means_corr <- practice_means_corr %>% 
  rename(Practice = practice) %>% 
  dplyr::select(-c(estimate, conf.low, conf.high)) %>% 
  relocate (Practice, .before = Norm) %>% 
  relocate (p.value, .after = last_col())

@@

# breadcrumbs:
# need to figure out whether I can rotate a page in papaja
# I need to use apa_tables.... (in line with papaja)
# EK - You can rotate the table, but I don't think it will rotate the page and it won't
# carry over into word

@@

<!-- I imagine we will remove the p.value column, but we might want this for now.  -->
<!-- It's not clear which stat the pvalue relates to, I would support removing it  -->

>>>>

In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm. However, the extent to which participants endorsed open science norms varied substantially across different practices. Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing 'agree'). They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items varied between 3.5 and 4. On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.

<!--MW: The paragraphs above contain some numeric info that's written in manually rather than being R outputs (e.g., "three", "seven") 
Not sure if that's a worry. JB: It sort of has to be because a) it's a holistic summary
and b) APA requires numbers below 10 to written out.
-->

<!-- JB: More of a concern for me is that we don't say anything about the 
correlations. If we aren't going to say anything about them at all, we can 
include them as a supplemental material? We preregistered them, so we have to 
include them, but we don't really have to say anything about them.-->

@@

# clean up the tibble                          
practice_means_corr <- practice_means_corr %>% 
  relocate (practice, .before = Norm) %>% 
  relocate (p.value, .after = last_col())

practice_means_corr <- practice_means_corr %>% 
  rename(Practice = practice) %>% 
  rename("Correlation p-value" = p.value) %>% 
  dplyr::select(-c(estimate, conf.low, conf.high))

@@

# need to figure out whether I can rotate a page in papaja
# EK - You can rotate the table, but I don't think it will rotate the page and it won't
# carry over into word. 
# JB: Moving correlations to a supplement will sove the problem I'm trying to resolve anyway...

@@

<!-- I imagine we will remove the p.value column, but we might want this for now.  -->
<!-- It's not clear which stat the pvalue relates to, I would support removing it  -->
<!-- JB: I've changed the heading of the p.value column for clarity. If we pull the corrs out
into a new table in the supplemental material, then we will want the p-value with it. -->
